\documentclass[a4paper,12pt]{article}

\usepackage{enumitem}
\usepackage{marvosym}
\usepackage{tabularx} % fancy tables
\usepackage[margin=1cm]{geometry}
\usepackage{fontspec} % for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} % other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} % better formatting of the A4 page
\usepackage{titlesec} % custom \section

% Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\titleformat{\section}{\large\scshape\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
% Tweak a bit the top margin
\addtolength{\voffset}{-1.0cm}
% Tweak a bit the left margin
\addtolength{\oddsidemargin}{-1.0cm}


%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%% WATERMARK TEST [**not part of a CV**]---------------
% \font\wm=''Baskerville:color=787878'' at 8pt
% \font\wmweb=''Baskerville:color=FF1493'' at 8pt
% {\wm
% 	\begin{textblock}{1}(0,0)
% 		\rotatebox{-90}{\parbox{500mm}{
% 			Typeset by Austin Jones with \XeTeX\  \today\
% 		}
% 	}
% 	\end{textblock}
% }

\pagestyle{empty} % non-numbered pages

%--------------------TITLE-------------

% Name
\par{\centering{\Huge Austin Jones}\smallskip{}
% Address
\par{\small \textsc{Address:} 201 S Central St, Knoxville, TN \---
% Phone
\small \textsc{Phone:} 615\--962\--3732\\
% Email
\textsc{Email:} \href{mailto:ajones53.aj@gmail.com}{ajone239@vols.utk.edu} \---
% Github
\textsc{GitHub:} \href{https://github.com/ajone239}{https://github.com/ajone239}
} \smallskip{}
% Summary
\par{\textbf{\underline{Objective}}: Software Engineer with experience in Embedded Software and Cloud Development looking for cool problems to solve.
Currently looking for employment starting Dec 2023.
}\smallskip}{}


%--------------------SECTIONS-----------------------------------

% Section: Skills
\section{Skills}
\begin{tabularx}{\textwidth}{rl}
   Cloud Technologies: & Docker, K8s, AWS, GitHub Actions, Postgres \\
   Embedded Technologies: & ARM MCUs, Xilinx FPGAs/MPSoCs \\
   Project Management: & GitHub, GitLab, Jira, Confluence, Agile \\
   Languages: & C, Rust, C++, Go, Shell, Python, VHDL \\
\end{tabularx}

% Section: Education
% degrees
\section{Education}
\begin{tabularx}{\textwidth}{lXr}
   \textbf{University of Tennessee Knoxville} & & Graduation: Dec 2021\\
   Bachelor of Science in \textsc{Computer Engineering} &  & \normalsize \textsc{Gpa}: $4.0/4.0$\\
\end{tabularx}

% work done in academic spaces
\begin{tabularx}{\textwidth}{r|X}

   \textsc{Dec 2021 \--} & \textbf{Engineering Professional Practice Office} \-- University of Tennessee\\
   \textsc{Aug 2019} & \emph{Student Ambassador}\\
   & \small{Assist UT engineering students to improve resumes, interview/inter-personal skills, and overall professional skills.
            Work with other ambassadors to facilitate networking events and career fairs.
   }\\

   \multicolumn{2}{c}{} \\

\end{tabularx}

% Section: Work Experience
% describe technical things that you've done for companies here
\section{Work Experience}

%
% PolySign
%
\begin{tabularx}{\textwidth}{r|X}
   \textsc{Nov 2023 \--} & \textbf{PolySign} \-- Remote \\
   \textsc{Jan 2022} & \small{Collaborated with many teams across multiple products and technologies to build out features and products for a Digital Asset Custodian in the quickly evolving Cryptocurrency market.} \\
   & \emph{\textbf{Senior Software Engineer}}: Jan 2023 \-- Nov 2023 \\
   & \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
        % Backend
        \item Contributed to Escrow feature of Python microservice backend:
            \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
              %% Split Escrow
              \item Redesigned feature data model to increase robustness.
              \item Designed a new data flow to allow for more flexibility in the feature.
              %% Two Sided Escrow
              % General
              \item Found, ticketed, and worked on tech debt as it was found.
            \end{itemize}
        % Web3 hacking
        \item Implemented an end-to-end POC for an unreleased feature across multiple projects.
        % HSM
        \item Worked on legacy C/Rust codebase to support features in other products.
        % Soft skills
        \item Performed monthly Dev-on-Call rotations debugging live issues across multiple environments including: dev, testing, pre-prod, and prod.
        \item Planned, hosted, and participated in a company wide Hackathon.
        \item Organized and hosted an engineering reading club.
      \end{itemize}\\
   & \emph{\textbf{Software Engineer}}: Jan 2022 \-- Dec 2022 \\
   & \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
        % Hot wallet
        \item Helped stand up a green field project in Rust aimed at performing fast, distributed multiparty compute signing:
            \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
              \item Designed fully asynchronous architecture for distributed message signing.
              \item Overhauled network stack to use Tokio's Tonic gRPC over VirtioVsock Sockets.
              \item Redesigned CI/CD Pipeline to minimize redundancy in builds, regression testing, and integration testing.
              \item Integrated with main product as a POC.
            \end{itemize}
      \vspace{-0.5cm}
      \end{itemize}\\
\end{tabularx}

%
% Garmin
%
\begin{tabularx}{\textwidth}{r|X}
   \textsc{Aug 2021 \--} & \textbf{Garmin International} \-- Olathe, KS\\
   \textsc{May 2021} & \emph{Embedded Software Intern}\\
   & \small{Developed code for microcontroller to control power on logic for an unreleased product.
      \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
        \item Utilized MCU to monitor main board status and determine the power state of the board.
        \item Referenced PCB schematics and MCU documentation to integrate software and hardware.
        \item Gained strong familiarity with ARM/STM microcontrollers.
      \vspace{-0.5cm}
      \end{itemize}}\\
\end{tabularx}

%
% Siemens
%
\begin{tabularx}{\textwidth}{r|X}
   \textsc{Nov 2021 \--} & \textbf{Siemens Molecular Imaging} \-- Knoxville, TN\\
   \textsc{Jan 2019} & \emph{Electrical R\&D Intern}\\
   & \small{Conduct projects, both individually and collaboratively, to provide value to the ER\&D team:
      \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
         \item Presented findings from work to a large technical audience to demonstrate the validity of a new system architecture.
         \item Long term projects:
            \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
               \item Utilize a Xilinx MPSoC to test limitations of ARM Core processing vs an FPGA implementation to assess cost reductions.
               \item Used multiple Raspberry Pis with off the shelf networking hardware to conduct data path tests and compare the bandwidth with current custom solutions.
               \item Work with a team of engineers using GitLab to write various driver code for a custom Linux image.
               \item Developed Firmware, Embedded Software, and Application Software for a unit test fixture that is used during production of PET electronics.
               \item Collaborated with a fellow intern to build a GUI Application that monitored and report the status of and entire system including all sub-assemblies.
            \end{itemize}
         \item Assist engineers with general tasks (e.g.\ wiring, testing, Python scripts, documentation).
      \vspace{-0.5cm}
      \end{itemize}}\\
\end{tabularx}

% Section: Scholarships and additional info
%% \section{Scholarships and Honors}
%% \begin{tabularx}{\textwidth}{lX}
%%    \textsc{May 2019} & Gonzalez Family Awards for Outstanding Computer Engineering Junior\\
%%    \textsc{Aug 2019} \-- \emph{Current} & S. T. Harris Scholarship\\
%%    % \textsc{Aug 2019} \-- \emph{Current} & Herschel C. \& Louise Runnion Brand Engineering Scholarship\\
%% \end{tabularx}

\section{Interests and Hobbies}
\begin{itemize}[topsep=2pt,itemsep=2pt,partopsep=2pt, parsep=2pt]
   \item Custom Mechanical Keyboards, Basic Electrical Projects, Competitive Programming
   \item Chess, Go, Reading, Cooking
   \item Rock Climbing, Cycling, Specialty Coffee
\end{itemize}

\end{document}
