\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{enumitem}
\usepackage{marvosym}
\usepackage{tabularx} % in the preamble
\usepackage[margin=1cm]{geometry}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.0cm}
\addtolength{\oddsidemargin}{-1.0cm}


%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

%--------------------TITLE-------------
\par{\centering{\huge Austin Jones \\
\small \textsc{Address:} 1004 Game Day Way, Apt 201\\
\small \textsc{Phone:} 615\--962\--3732 \---
\textsc{Email:} \href{mailto:ajone239@vols.utk.edu}{ajone239@vols.utk.edu}
} \smallskip
\par{\textbf{Objective}: Computer Engineering Senior looking for a summer internship May 2021 or full time position for Jan 2022.
%Networking solutions sounds fucking stupid
Interested in working with Embedded Systems, IoT, Networking.
}\smallskip}


%--------------------SECTIONS-----------------------------------

%Section: Education
\section{Education}
\begin{tabularx}{\textwidth}{lXr}
   \textbf{University of Tennessee Knoxville} & & Anticipated Graduation: Dec 2021\\
   Bachelor of Science in \textsc{Computer Engineering} &  & \normalsize \textsc{Gpa}: 4.0/4.0\\
\end{tabularx}

%Section: Work Experience at the top
\section{Work Experience}
\begin{tabularx}{\textwidth}{r|X}
   \emph{Current} & \textbf{Siemens Molecular Imaging} \-- Knoxville\\
   \textsc{Jan 2019} & \emph{Electrical R\&D Intern}\\
   & \small{Conduct work on projects, both solo and team, to provide value to the ER\&D team:
      \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=0pt,partopsep=1pt, parsep=1pt]
         % include head of r&d?
         \item Presented findings from work to a large technical audience to demonstrate the validity of a new system architecture.
         \item Lead long term projects:
            \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=0pt,partopsep=1pt, parsep=1pt]
               \item Utilize a Xilinx MPSoC to test limitations of ARM Core processing vs an FPGA implementation to assess cost reductions.
               \item Use many Raspberry Pis with off the shelf networking hardware to conduct data path tests and compare the bandwidth with current custom solutions.
               \item Work with a team of Engineers, collaborating with GitLab to write various driver code for a custom Linux image.
               \item Create a functional test to insure proprietary hardware functioned to spec.
               \item Collaborate with fellow intern to make a suite of software tools to monitor systems for various needs and engineers.
            \end{itemize}
         \item Update and Maintain Engineering Documentation for various projects.
         \item Assist Engineers with general tasks (e.g.\ wiring, testing, Python scripts to process files)
      \end{itemize}}\\
\end{tabularx}

\section{Skills}
\begin{tabularx}{\textwidth}{rl}
   Working Knowledge: & Xilinx FPGAs, Petalinux, Intel FPGAS,.NET, POSIX\\
   Serious Languages:& C++, C, C\#, Python, Shell, VHDL, \LaTeX{}\\
   Recreational Languages:& Rust, Haskell, Groff, BF \\
   Office Skills: & Excel, GIMP, Visio\\
\end{tabularx}

\section{Academic Experience}
\begin{tabularx}{\textwidth}{r|X}

   \emph{Current} & \textbf{Engineering Professional Practice Office} \-- University of Tennessee\\
   \textsc{Aug 2019} & \emph{Student Ambassador}\\
   & \small{Work with students to improve resumes, interview/inter-person skills, overall professional skill to increase the number of internships and coops attained by the students at UT\@.
   }\\

   \multicolumn{2}{c}{} \\

   \textsc{Apr 2019} & \textbf{Proof of Concept Password Manager} \-- University of Tennessee\\
   & \emph{COSC 302 Project}\\
   & \small{Collaborated with a group of peers, using Github, to create a functional Chrome extension that manages a user's passwords for multiple sites.
            Parsed web pages to find password and username fields and stored users encrypted data in the cloud.
            The data was encrypted with the RC4 symmetric stream based encryption algorithm.
   }\\
\end{tabularx}

%Section: Scholarships and additional info
\section{Scholarships and Honors}
\begin{tabularx}{\textwidth}{lX}
   \textsc{Aug 2019} \-- \emph{Current} & S. T. Harris Scholarship\\
   \textsc{Aug 2019} \-- \emph{Current} & Herschel C. and Louise Runnion Brand Engineering Scholarship\\
   \textsc{May 2019} & Gonzalez Family Awards for Outstanding Computer Engineering Junior\\
\end{tabularx}

\section{Interests and Hobbies}
\begin{itemize}[topsep=1pt,itemsep=0pt,partopsep=1pt, parsep=1pt]
   \item Raspberry Pi, Arduino, Self-Hosting, IoT Projects
   \item VolHacks, Mechanical Keyboards, Basic Electrical projects
   \item Rock Climbing, Cooking, Digital Art % it's dumb but hey.
\end{itemize}

\end{document}
