\documentclass[a4paper,11pt]{article}

%A Few Useful Packages
\usepackage{enumitem}
\usepackage{marvosym}
\usepackage{tabularx} % in the preamble
\usepackage[margin=1cm]{geometry}
\usepackage{fontspec} 					%for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} 				%better formatting of the A4 page
\usepackage{titlesec}					%custom \section

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%CV Sections inspired by:
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\large\scshape\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
%Tweak a bit the top margin
\addtolength{\voffset}{-1.0cm}
% Left align
\addtolength{\oddsidemargin}{-1.0cm}


%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

%WATERMARK TEST [**not part of a CV**]---------------
%\font\wm=''Baskerville:color=787878'' at 8pt
%\font\wmweb=''Baskerville:color=FF1493'' at 8pt
%{\wm
%	\begin{textblock}{1}(0,0)
%		\rotatebox{-90}{\parbox{500mm}{
%			Typeset by Alessandro Plasmati with \XeTeX\  \today\ for
%			{\wmweb \href{http://www.aleplasmati.comuv.com}{aleplasmati.comuv.com}}
%		}
%	}
%	\end{textblock}
%}

\pagestyle{empty} % non-numbered pages

%--------------------TITLE-------------
\par{\centering{\huge Austin Jones \\
\small \textsc{Address:} 1004 Game Day Way Apt 201, Knoxville, TN \---
\small \textsc{Phone:} 615\--962\--3732 \\
\textsc{Email:} \href{mailto:ajone239@vols.utk.edu}{ajone239@vols.utk.edu} \---
\textsc{Github:} \href{https://github.com/ajone239/}{github.com/ajone239/}
} \smallskip\par}


%--------------------SECTIONS-----------------------------------

% Section: Skills
\section{Skills}
\begin{tabularx}{\textwidth}{rl}
   Working Knowledge: & Xilinx FPGAs, Xilinx MPSoCs, Petalinux, Intel FPGAS, POSIX\\
   Professional Languages:& C++, C, C\#, Python, Shell, VHDL\\
   Recreational Languages:& Rust, Haskell, BF, Groff \\
   Office Skills: & Excel, GIMP, Visio, \LaTeX{}\\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section: Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\begin{tabularx}{\textwidth}{lXr}
   \textbf{University of Tennessee Knoxville} & & Anticipated Graduation: Dec 2021\\
   Bachelor of Science in \textsc{Computer Engineering} &  & \normalsize \textsc{Gpa}: 4.0/4.0\\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Academic Experience}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{tabularx}{\textwidth}{r|X}

   \emph{Current} & \textbf{Engineering Professional Practice Office} \-- University of Tennessee\\
   \textsc{Aug 2019} & \emph{Student Ambassador}\\
   & \small{Assist UT engineering students to improve resumes, interview/inter-person skills, and overall professional skill.
            Work with other ambassadors to facilitate networking vents and career fairs.
   } \\

   \multicolumn{2}{c}{} \\

   \textsc{Jan 2021} & \textbf{Light Sign with Web Server Control} \-- Personal Project\\
   & \small{Controlled an LED Array to display text specified on a web page.}\\

   \multicolumn{2}{c}{} \\

   \textsc{Apr 2019} & \textbf{Password Manager Browser Extension} \-- University of Tennessee\\
   & \emph{Data Structures and Algorithms Final Project}\\
   & \small{Collaborated with a group of peers using Github to create a functional Chrome extension that manages a user's passwords for multiple sites.}\\

   \multicolumn{2}{c}{} \\

   \textsc{Apr 2019} & \textbf{Render Component for Firmware Based Pong} \-- University of Tennessee\\
   & \emph{Digital Systems Design Final Project}\\
   & \small{Reimplemented the retro game Pong on an FPGA using VHDL\@.
            Component was implemented to read the game state and render all game objects and scores.
            }\\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section: Work Experience at the top
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experience}
\begin{tabularx}{\textwidth}{r|X}
   \emph{Current} & \textbf{Siemens Molecular Imaging} \-- Knoxville\\
   \textsc{Jan 2019} & \emph{Electrical R\&D Intern}\\
   & \small{Conduct projects, both individually and collaboratively, to provide value to the ER\&D team.
            Work involved both product and research driven projects.
            Product driven work would involve sustaining, documentation, and more inter-departmental communication.
            Research involved proof of concept projects that would extrapolate to larger implementation.
      \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
         \item Presented findings from work to a large technical audience to demonstrate the validity of a new system architecture.
         \item Lead long term projects:
            \begin{itemize}[leftmargin=20pt,topsep=1pt,itemsep=1pt,partopsep=0pt, parsep=1pt]
               \item Utilize a Xilinx MPSoC to test limitations of ARM Core processing vs an FPGA implementation to assess cost reductions.
               \item Used multiple Raspberry Pis with off the shelf networking hardware to conduct data path tests and compare the bandwidth with current custom solutions.
               \item Work with a team of Engineers using GitLab to write various driver code for a custom Linux image.
               \item Created a functional test to insure proprietary hardware functioned to spec.
            \end{itemize}
         \item Update and maintain Engineering Documentation for various projects.
         \item Assist engineers with general tasks (e.g.\ wiring, testing, Python scripts to process files)
      \vspace{-0.5cm}
      \end{itemize}}\\
\end{tabularx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Section: Scholarships and additional info
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scholarships and Honors}
\begin{tabularx}{\textwidth}{lX}
   \textsc{May 2019} & Gonzalez Family Awards for Outstanding Computer Engineering Junior\\
   \textsc{Aug 2019} \-- \emph{Current} & S. T. Harris Scholarship\\
   \textsc{Aug 2019} \-- \emph{Current} & Herschel C. and Louise Runnion Brand Engineering Scholarship\\
\end{tabularx}

\end{document}
