\documentclass[a4paper,12pt]{article}

\usepackage{enumitem}
\usepackage{marvosym}
\usepackage{tabularx} % fancy tables
\usepackage[margin=1cm]{geometry}
\usepackage{fontspec} % for loading fonts
\usepackage{xunicode,xltxtra,url,parskip} % other packages for formatting
\RequirePackage{color,graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[big]{layaureo} % better formatting of the A4 page
\usepackage{titlesec} % custom \section

% Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\titleformat{\section}{\large\scshape\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{3pt}{3pt}
% Tweak a bit the top margin
\addtolength{\voffset}{-1.0cm}
% Tweak a bit the left margin
\addtolength{\oddsidemargin}{-1.0cm}


%-------------WATERMARK TEST [**not part of a CV**]---------------
\usepackage[absolute]{textpos}

\setlength{\TPHorizModule}{30mm}
\setlength{\TPVertModule}{\TPHorizModule}
\textblockorigin{2mm}{0.65\paperheight}
\setlength{\parindent}{0pt}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

%--------------------Header-------------

% Name
\Huge Austin Jones\smallskip{} \\
% Address
\small \textsc{Address:} 201 S Central St, Knoxville, TN \\
% Phone
\small \textsc{Phone:} 615\--962\--3732 \\
% Email
\textsc{Email:} \href{mailto:ajones53.aj@gmail.com}{ajones53.aj@gmail.com} \\
% Github
\textsc{GitHub:} \href{https://github.com/ajone239}{https://github.com/ajone239} \\

% Today
\today

% Salutation
Dear Hiring Manager,

% Intro
I am writing you to apply to the CORE TECH - NATIVE FRAMEWORK \& TOOLS INTERN role at Discord.
I've been working in the industry for about 2 years now, but I've nearly 5 years of engineering experience given the work I did in internships.
You may wonder why I'm applying for an internship 2 years out of college.
Frankly, Discord seems like a wonderful place to work and all the open positions that align with my skill set require more experience than a team of me could amass.
Discord is an enticing place to work as it melds all the computer problems I love to work on.
I like working on problems with high data throughput, distributed systems, and performance requirements that require systems knowledge.
It is a simple concept (every programmer wrote a simple chat server in university) but at a scale that requires bleeding-edge solutions and technology.
I've long followed the Discord blog and all the articles detail problems and solutions that interest and excite me.

% School + Internships
At the University of Tennessee, I studied Computer Engineering, so my studies ranged from embedded software to systems-level programming.
I've always loved working close to the metal, be that on a microcontroller or close to the application/operating systems barrier.
At my first internship at Siemens, I worked on many projects ranging up and down the stack.
From GUI test applications to FPGA firmware, I had my hands on many long-term projects; some of which are likely still in use.
Consequently, I was also responsible for presenting and communicating my work/findings, requiring effective understanding and organization of ideas to show to audiences of varying technicality.
At Garmin, my efforts were more focused.
In the summer, I became very acquainted with a particular model of STM ARM microcontroller and used it to write the power-on logic for a new product.
My sole responsibilities were to realize this software, but it involved communicating with the rest of the team, reading chip specs, much code review, and using schematics to inform firmware decisions.

% Work
My time in the industry was spent working on cloud-based microservice applications.
At Polysign, I worked almost exclusively in the cloud, but this still yielded very transferable skills.
As it was a start-up, I was often handed the reigns on designs or even full features.
The fast and agile development process allowed for whole top-level designs to be usurped for better ones.
Team cross-talk and integration between teams weren't common but vital to bringing up features, products, or debugging production incidents.
Technologies across the firms were new and abundant meaning that picking up a small task may also involve learning two or three new technologies and how to use them.
This kept me on my toes for entering new projects, expecting nothing and turning to testing to get my footing.

% Conclusion
Thank you for taking the time to read my application and considering me for this position.
If you've any questions, feel free to reach me with the information above.
I'm sure my mixture of skills and work ethic could be a great fit for this role.


% Letter ending and signature
Best,
Austin Jones

\end{document}
